Reionization Planck 2018 Notes

### 2020-07-07 results/notes.tex
Updates from Overleaf

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_relike_tanh_tau_dz0p5_1D_direct_vs_fortran_and_python_kde.png}
\caption{DEBUGGING - updated the KDE tanh results to have tanh dz = 0.5. Also added in faint blue lines Gaussian and convolved Gaussian with $\sigma \rightarrow \sigma$.
}
\label{fig:}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_relike_tanh_tau_dz0p5_1D_direct_vs_fortran_and_python_kde_with_grid_test.png}
\caption{DEBUGGING - tanh dz = 0.5 for all curves. ...)
}
\label{fig:}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_relike_tanh_tau_dz0p5_1D_direct_vs_fortran_and_python_kde.png}
\caption{DEBUGGING - updated the KDE tanh results to have tanh dz = 0.5. Also added in faint blue lines Gaussian and convolved Gaussian with $\sigma \rightarrow \sigma \sqrt(1+f)$.
}
\label{fig:}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_relike_tanh_tau_dz0p5_1D_direct_vs_fortran_and_python_kde_with_grid_test.png}
\caption{NEW - added blue circles which are evaluating the Fortran KDE code on a grid of 100 values of $\tau$. This shows that the extra smoothing in the red curve (Fotran MCMC code) vs green (python grid evaluations) are \textbf{likely due to the smoothing used in getdist to make the red curve}.
}
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_relike_tanh_tau_dz0p5_1D_direct_vs_fortran_vs_mock_gaussian_fp10_fp14.png
}
\caption{NEW - comparing f = 0.10 and 0.14 in python KDE (latest version) against an example of gaussian smoothing with 0.10, 0.14 on a symmetric Gaussian function.
}
\label{fig:}
\end{figure}
